msb106_assignment

### 2024-01-24 msb106_assignment.qmd
k

>>>>

```{r}
maindata %>%
  group_by(classification_nr, TIME_PERIOD) %>%
  summarise(mean_value = mean(OBS_VALUE, na.rm = TRUE)) %>%
    mutate(demeaned_value = mean_value/first(mean_value)) %>%
  ggplot(aes(x = TIME_PERIOD, y = demeaned_value, color = classification_nr)) +
  geom_line() +
  labs(x = "År",
       y = "Gjennomsnittlig Befolkningsvekst",
       color = "Regioner") +
  theme_minimal()
```

```{r}
maindata %>%
  filter(geo == "DE") %>%
  group_by(classification_nr, TIME_PERIOD) %>%
  summarise(mean_value = mean(OBS_VALUE, na.rm = TRUE)) %>%
    mutate(demeaned_value = mean_value/first(mean_value)) %>%
  ggplot(aes(x = TIME_PERIOD, y = demeaned_value, color = classification_nr)) +
  geom_line() +
  geom_point() +
  labs(x = "År",
       y = "Gjennomsnittlig Befolkningsvekst",
       color = "Regioner") +
  theme_minimal()
```
